Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-02-22 pkg/disttree/inst/draft/draft.Rnw
additional reference for Breiman and Cutler's random forests
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2036 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: d696b83c5fe4e3bac0f3b0cc16a8f1cafb3db3b9

%%% <TH> we need to be much more precise here: random forests is Breiman's and Cutler's
%%% random forest. Maybe it is better to not mention this method at any time. </TH>
Common forest models (such as Breiman and Cutler's randomForest) consist of 
trees only considering the mean of the distribution of the response variable. 
For that reason, changes in other parameters can only be detected if they 
are connected to changes in the location parameter, e.g. if they depend on 
the location parameter. As explained before, a distributional tree considers
scores for all distribution parameters. Therefore, a forest consisting of 
distributional trees can also capture separate effects in each of the 
distribution parameters. For that reason distributional forests are
now going to be introduced.

@@

\fixme{Avoid nocite, make all relevant citations properly in the text.}

\nocite{Seibold+Zeileis+Hothorn:2016, Seibold+Zeileis+Hothorn:2017, Yee:2010}
% Zeileis+Wiel+Hornik:2008, 
% Zeileis+Hothorn+Hornik:2010,

%\newpage
%\newpage
\bibliography{ref.bib}

@@

\section{Tree algorithm}
\label{treealgorithm}
The tree algorithm used in the applications discussed in this paper 
is explained in the following. For notational simplicity, the testing 
and splitting procedure is described for the root node with observations 
$\{y_i\}_{i = 1,\ldots,n}$, $n \in \mathbb{N}$. In each child node the 
corresponding subset of observations depends on the assignment made 
by the foregoing split.

>>>>

%%% <TH> we need to be much more precise here: random forests is Breiman's and Cutler's
%%% random forest. Maybe it is better to not mention this method at any time. </TH>
Common forest models such as the original forest technique by 
\cite{Breiman+Cutler:2004} consist of trees only considering the mean of the 
distribution of the response variable. For that reason, changes in other 
parameters can only be detected if they are connected to changes in the 
location parameter, e.g. if they depend on the location parameter. 
As explained before, a distributional tree considers scores for all 
distribution parameters. Therefore, a forest consisting of 
distributional trees can also capture separate effects in each of the 
distribution parameters. For that reason distributional forests are
now going to be introduced.

@@

\bibliography{ref.bib}

@@

\section{Tree algorithm}
\label{treealgorithm}
The tree algorithm used in the applications discussed in this paper 
is going to be explained following the ideas presented in 
\cite{Seibold+Zeileis+Hothorn:2017}. For notational simplicity, the testing 
and splitting procedure is described for the root node with observations 
$\{y_i\}_{i = 1,\ldots,n}$, $n \in \mathbb{N}$. In each child node the 
corresponding subset of observations depends on the assignment made 
by the foregoing split.
